On Combinatorial Games and de Bruijn Sequences

### 2016-11-05 infdebruijn.tex
aaa

@@

\item{Case 3.} $\sigma z_2\notin L_n$  and $x'=0^l$. In this case, $b_1(\sigma z_2)$ = $0^ly(\sigma xy)^{r+1}$. Write $w''=(\sigma xy)^{r+1}0^ly$ (is it a key-word?). Then, $v0^l$ is a subword of $b^*(w'')w''$ (really?).

>>>>

\begin{lemma}
Let $w=0^ly(x0^ly)^{r+1}$ be an $n$-length word such that $y\notin \{0\}^*$. Then, $w$ is not a key-word. 
\end{lemma}

\begin{proof}
Assume for a contradiction that $w$ is a key-word of length $n$, and take a maximal $t\in \N$ such that $x0^ly=x'(0^ly)^{t+1}$. First, we note that $x'\neq \varepsilon$. Indeed, if $x'=\varepsilon$, then $w=(0^ly)(0^ly)^{t(r+1)}$, a periodic word, and $w$ then is not an key-word.

Now we claim that $|x'|<|y|$.
\end{proof}

@@

\item{Case 3.} $\sigma z_2\notin L_n$  and $x'=0^l$. In this case, $b_1(\sigma z_2)$ = $0^ly(\sigma xy)^{r+1}$. Note that $w=0^ly(x''0^ly)^{r+1}$ and use Lemma \ref{} to achieve a contradiction.
